Comprehensive Quality-Aware Automated Semantic Web Service Composition

### 2017-01-30 paper.tex
update

\begin{document}
\maketitle
\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major challenges faced by researchers, semantic matchmaking and QoS optimisation. Semantic matchmaking aims to discover interoperable web services that can interact with each other to provide rich functionalities through language understanding and reasoning. QoS optimisation aims to optimise the non-functional requirement of service users, e.g., minimum cost, maximal reliability. Many scholars have looked into QoS optimisation problems in QoS-aware web service composition applying AI planning and Evolutionary Computation techniques. To meet users' requirement, one often needs to consider both semantic matchmaking quality and QoS simultaneously. Existing works on web service composition often concerns either semantic service composition or QoS-aware service composition. However, there are few works concerns both semantic matchmaking quality and QoS at the same time and achieve a more desirable tradeoff in consideration of both sides. Therefore, In this paper, proposed a general comprehensive quality model for semantic matchmaking quality and QoS. This model is also suitable to be tackled through EC algorithms, and we develop a PSO-based service composition approach with explicit support for the comprehensive model, which can generate a more desirable balanced web service composition that meet both semantic matchmaking quality and QoS requirement by comparing existing QoS evaluation model using benchmark dataset. We also conduct an experiment shows our PSO-based method performs better in finding more optimised solution by comparing one existing GP-based method.

@@

\textit{Web service composition} pertains to a combination of multiple web services to provide a value-added composition service that accommodates customers' arbitrarily complex requirements. This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems. Due to the increase of the number of large-scale enterprise applications, the number of Web services has increased substantially and unprecedentedly. Therefore, manual and semi-automated web service composition are considered to be less efficient while automated web service composition enjoys less human intervention, less time consumption, and high productivity.

@@

Existing works on service composition focus mainly on addressing the one of challenges above. A lot of works have been conducted to optimise the quality of compositions under a pre-defined abstract workflow, which is generally considered as \textit{semi-automated Web service composition} approach \cite{parejo2008qos,bahadori2009optimal}. Meanwhile, many research works consider the possibility of generating a composition plan automatically in discovering and selecting suitable web services, which are considered to be NP-hard \cite{moghaddam2014service}. \textit{Semantic web services composition} is distinguished from the syntactic service composition, with the hope of eliminating conflicts by the semantic level of web services. In the past few years, substantial works have been done on semantic web service composition \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune}. However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously. To a given service request, the quality of service composition solution depends on both QoS and quality of semantic matchmaking.

The overall goal of this paper is to \textit{develop an comprehensive approach to automated QoS-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}. Particularly, this paper extends existing works of QoS-aware service composition by considering both QoS optimisation and semantic matchmaking quality optimisation in our proposed comprehensive quality model. Particle Swarm Optimisation (PSO) has show its promise in searching near-optimised service composition solutions \cite{da2016particle}. We will propose a PSO-based service composition approach using our comprehensive quality model to measure semantic matchmaking in automated semantic web service composition. We will achieve three objectives in this work as follows:

@@

 \item To propose a PSO-based service composition algorithm that utilises the proposed quality model. To do that we will first propose a representation of semantic service composition, which can model the quality of semantic matchmaking and QoS together. A particle is then used to represent a queue of services that can be used to decoded into a near-optimised semantic service composition solution.

 \item To evaluate our proposed approach, we conduct experiment to compare our comprehensive quality model with QoS evaluation model, we also compare an one existing GP approach with our approach using our comprehensive model. Both comparison utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}

@@

\cite{boustil2014semantic,mier2015integrated, bansal2016generalized} captures the semantics of the parameters of web services using some kind of logic (e.g., description logic) for enabling semantic web service composition, where the number of web services or length of the graph is minimised to reach the optimised graph-based composition solutions. However, these approaches always need to improve their scalability for a large number of web services, and the evaluation method does not fit for today's customers' requirements properly.

A heuristic service composition method is proposed by Qi et al. \cite{qi2010combining}for QoS-aware web service composiiton, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal for QoS consideration. but obviously there exists scalability problem for enumeration techniques.

Evolutionary Computation (EC) techniques are used to improve the scalability for solving NP-hard problems. Gupta et al. \cite{gupta2015optimization} employ an Genetic Algorithm to the problem of QoS-ware web service composition, and a set of binary strings are used as individuals, which demands to be decoded into composition solutions. Genetic Programming are employed by  \cite{yu2013adaptive} with direct representation of composition solutions, the overall quality of solutions are measured by a fitness function that is liable for penalising infeasible solutions. A hyper approach employs both a greedy search algorithm and Genetic Programming (GP) is introduced in \cite{ma2015hybrid} to generate locally optimised solution with functionality correctness. In particularly, the greedy search is used to generate directed acrylic graph as composition solutions, which is further transferred to tree structure using unfolding techniques for initialisation and mutation during the evolutionary process. To eliminating the transformation process from DAG, A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of Directed Acyclic Graph(DAG) employing Graph-based evolutionary operators like crossover and mutation. PSO has shown its efficiency in solving combinatorial optimisation problems \cite{fukuyama2008fundamentals}, an indirect PSO-based approach was introduced in \cite{da2016particle}. An optimised queue is used as indirect representation as composition solution that decoding into Direct Acyclic Graph (DAG). These QoS-aware approaches does not consider semantic matchmaking quality, which could lead to over-general outputs to be produced by selected services, The finding is evidently supported by our first comparison experiment. In fact, customers' perspectives, application domains and ontology granularity all could have significant impact on the outputs requested by users. In some scenarios, the output is too broad to bear any specific meaning for the customers, even though those web services selected leads to a very good overall QoS.

Few works \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} employ EC technique for considering both semantic matchmaking quality and QoS simultaneously. Lecue et al. \cite{lecue2009optimizing} employ Genetic Algorithm for semi-automated web service composition considering semantic matchmaking quality and QoS, where the semantic matchmaking quality is measured the quality of semantic links that requires formal definition of ontology in Description logic. This evaluation takes huge cost and time for the domain experts to establish required ontology. Another GA-based approach work \cite{fanjiang2014semantic} employs a sequence of fitness functions are used in the binary selection of chromosomes, where semantic matchmaking quality is evaluate in two fitness functions considering concept similarity and parameter similarity respectively, However, different semantic matchmaking types are ignored in evaluation model. The work \cite{pop2009immune} as an immune-inspired web service composition approach employ indirect representation that a binary alphabet to encode a planning graph, where the semantic matchmaking quality is measured  by the similarity using information retrieval technique.

In summary, composition solutions from semantic web service composition does not consider QoS \cite{boustil2014semantic,mier2015integrated, bansal2016generalized}, and QoS-aware web service composiiton \cite{da2016particle,da2015graphevol,yu2013adaptive, gupta2015optimization,qi2010combining,ma2015hybrid} does not consider distinguished matchmaking quality in their fitness function. Few works do consider both quality aspects, but some limitations lie in semi-automated approach \cite{lecue2009optimizing}, less general semantic quality measurement \cite{lecue2009optimizing, pop2009immune}, or semantic matchmaking types ignorance \cite{pop2009immune}. In addition, experiments design for  \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} are not conducted using benchmark dataset for the scalability, only small datasets are utilised that might suffer scalability. Results analysis for \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} also do not evidently point out what desired balance could be reached by considering semantic matchmaking quality and QoS. Therefore, we proposed a general comprehensive quality model which achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS to fill the gaps discussed above, and then we proposed a POS-based method with explicit support for the comprehensive model, and evaluate its performance by comparing with one existing GP-based approach.

@@

The aim of web service composition is to fulfil customers' requirements, which could be denoted as a composition goal: $Comp.G(F(I_{T}, O_{T}), NF(QoS_{T}))$. This overall composition goal is demonstrated in two parts: functional part and non-functional part. The functional part is defined by a given task input and a desired task output. The nonfunctional part specifies QoS. To accomplish the composition goal, two stages are involved, services discovery and service selection. Service discovery is to find matching web services: $S_{n}(F(I_{S}, O_{S}), NF(QoS_{S}))$ from a Service Repository: $\mathcal{S}$ $=  \{S_{1}, S_{2},..., S_{n} \}$ for the given $I_{T}$. If no atomic web service could satisfy the composition goal, a composition of web services will be found to meet $Comp.G$. To ensure the composition solution returns the desired $Comp.G$, we use a quality model that take care of QoS and semantic matchmaking quality.

@@

\section{Comprehensive Quality Model}\label{qswsc_approach}
In this section, we propose a comprehensive quality-aware service model to achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS for semantic web service composition.

\subsection{Semantic Web Service matchmaking Type}\label{semantic Web service Discovery}
The semantic service matchmaking aims to discover appropriate services from service repository. A semantic web service is defined by $S(F(I_{S}\in C_{1}, O_{S}\in C_{2}), NF(QoS_{S}))$, where both Input and Output are linked to concept $C_{1}$ and $C_{2}$ in an ontology $O$ respectively, satisfying $O=\{C, Taxonomy\}$. A web service matching process is to match the output and input concepts of two services according to the Taxonomy within an ontology. To measure the quality of semantic matchmaking, different matching levels are typically considered in the literature \cite{paolucci2002semantic}. To understand these levels, let us define two web services associated with concept-related parameters in a particular domain. $S_{1}$ $(F(I_{S}\in C_{1}, O_{S}\in C_{2}), NF(QoS_{S}))$ and  $S_{2}$ $(F(I_{S}\in C_{3}, O_{S}\in C_{4}), NF(QoS_{S}))$ and an ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$. The matching levels to be considered are:

\begin{itemize}
\item \textit{Exact} ($\equiv$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Exact match ($ O_{S} \in S_{1} \equiv I_{S} \in S_{2}$), if  Concept $C_{2}$ and Concept $C_{3}$ are equivalent.
\item \textit{Plugin} ($\sqsubseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Plugin match ($O_{S} \in S_{1} \sqsubseteq_{n} I_{S} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of children concepts ($n=1$ stands for direct children).
\item \textit{Subsume} ($\sqsupseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Subsume matched($O_{S} \in S_{1} \sqsupseteq_{n} I_{S} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of  Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of parent concepts ($n=1$ stands for direct parent).
\item \textit{Fail} ($\perp$). Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are not matched (Fail) ($O_{S} \in S_{1} \perp I_{S} \in S_{2}$), if none of the previous matches discovered.
\end{itemize}

@@

\subsection{Comprehensive Quality Model}\label{qualityModel}
In this paper, we propose a comprehensive quality model to evaluate the overall quality of semantic web service composition. This model overcome the disadvantages of current prevailing QoS-aware optimisation that ignores quality of semantic matchmaking.

@@

\textbf{Semantic web matchmaking quality model}. Due to the discretisational characteristics of different match types and values assigned to matching types that driven by the cost of data integration and manipulation \cite{lecue2009optimizing}, partial ordering match types are considered to be one factor for quality of parameter matchmaking, denoted as $mt_{p}$,  For example, Exact matching type demands less time for computation compared to that of Plugin match. Another factor in our proposed model is concept similarity, which could be evaluated based on the edge counting method defined in \cite{shet2012new}. This formula (\ref{equation1}) is used to estimate the concept similarity between matching parameters, which is denoted as $s_{p}$. Therefore, given the quality of parameter matchmaking type and quality of parameter concept similarity, the quality of parameter matchmaking is defined by Formula (\ref{equation2}), where the value of $mt_{p}$ follows the same settings in \cite{lecue2009optimizing}. Particularly, 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection).

\begin{equation}
s_{P}{=} \frac{2N \cdot e^{-\lambda L/D} }{N_{1}+N_{2}}
\label{equation1}
\end{equation}

@@

Further more, semantic web service link represent services connections, where quality of semantic web service link $sm_{L})$ is considered to be semantic matching quality on service connection level by parameter aggregations. Therefore, $sm_{L}$ is defined in formula (\ref{equation3}), where $sm_{L}$ and $s_{L}$ are the average value of concept-related parameters quality in $mt_{P}$ and $s_{P}$ respectively.

@@

\textbf{Comprehensive quality model}. The comprehensive quality model consider both semantic matchmaking quality and QoS. The semantic matchmaking quality refers to the quality of semantic web service link. Consequently, the comprehensive quality model is defined in Formula (\ref{equation4}), which could be further broken down into Formula (\ref{equation5}). 
\begin{equation}
\label{equation4}
q_{cq} \stackrel{.}{=} (sm_ {L}, \  QoS_ {s})
\end{equation}
\begin{equation}
\label{equation5}
q_{cq} \stackrel{.}{=} (mt_ {L}, \  s_ {L}, \  a_{s},\  r_{s},\  c_{s},\  t_{s})
\end{equation}

\textbf{Semantic matchmaking quality aggregation}. The quality aggregation is defined based on the constructs of composition web services, in consideration of quality semantic web service link and QoS. The quality on composition solution is further calculated by following the formula (\ref{equation6})(\ref{equation7}), and QoS aggregation are discussed in Sect. \ref{Quality of Service and Composition Constructs}

@@

We defined our semantic web service composition solution as a weighted graph $WG = (V, E)$, where $V$ is a set of services as vertex: $V=\{S1, S2...Sn \}$ and $E$ is a set of edges $E = \{e_{1}, e_{2},... e_{n} \}$. Each edge is mapped to a semantic web service link, so each edge $e$ is associated with $sm_{L}$ as weight value as a pair value of quality values $mt_{L}$ and $s_{L}$ on the edge level, Here we provide an example of semantic web service composition, which is described in Fig. \ref{wscs}. The data of composition web service flows from the start to the end, where five web services involved and linked with each other using edge connections. Besides that, pair values that $mt_{L}$ and $s_{L}$ are calculated for all edges $e_{1}, e_{2},... e_{n}$ assigned as weights.

@@

PSO has shown its efficiency in solving combinatorial optimisation problems \cite{fukuyama2008fundamentals}. Therefore, we will employ a PSO-based approach, which is considered to be simple and efficient without penalising or repairing that often required by GP \cite{da2016particle}. Fig. \ref{overview} shows the overview of our approach with five steps. Step 1: The composition process is triggered by a composition goal defined in Subsection \ref{problemDes}, which describes customers requirements both semantic matchmaking quality and QoS. Step 2: This composition goal are used to discover all relevant web services, which lead to a shrunken service repository that is subsequently used by PSO as a searching space. Step 3: A weighted graph representation is randomly built up from the an initial service queue that mapped to the particle's location, interleaving with semantic matchmaking process utilising ontology-based index cache. In the weighted graph, graph edges are assigned with semantic matchmaking quality as weights. Step 4: The fitness value of the weighted graph is evaluated to update the position of particle under PSO algorithm in Sect. \ref{pso_algorithm}, where the position is mapped to the index of service queue. later on, the updated service queue is used to decode a new weighted graph as the composition solution. Step 4. Lastly, the best position found in the searching space is selected and decode into the final optimised solution. This PSO-based approach is similar to \cite{da2016particle}, but we employ weighted graphs as a different solution presentation with edges transferred from semantic web service links.

\subsection{Ontology-based Index Cached Optimisation}\label{indexCache}
In PSO, particles represent weighted graphs with edges and vertices associated with quality of semantic web service matchmaking and QoS respectively, the bottlenecks of generating weighted graph lie in building edges and nodes, which are related to the cost of semantic quality calculation and the size of service repository respectively. To effectively construct weighted graphs, we pre-calculate semantic matchmaking quality. The key idea of the index is to create a mapping from the output-related concepts to potentially matched input-related concepts while considering different levels of match types. Meanwhile, this index size could also be reduced by only considering the concepts related in the shrunken service repository, which means the index cache is filtered by those task-relevant web services. This optimised cache also contributes to less and constant time for weighted graphs building through the whole evolutionary process.

@@

\begin{algorithm}
 \setlength\hsize{0.9\linewidth}
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \SetKwFunction{generateWeightedGraph}{generateWeightedGraph}
 \SetKwProg{Procedure}{Procedure}{}{}
 \LinesNumbered
 \SetNlSty{}{}{:}
 \Input{relevant Web services $rws$}
 \Output{Optimised service queue $queue$,Optimised Weighted Graph $OPTWG$}
 Map each relevant service to an index in the particle's position vector\;
 Randomly initialise each particle in the swarm\;
  \While {max. iterations not met}{
     \ForEach{particles in the swarm}{
     $queue \leftarrow$ map particle's position vector to service\;
     $WG \leftarrow$ $generateWeightedGraph$()\;
	 Calculate the $WG$ fitness value\;

>>>>

\begin{document}
\maketitle
\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major challenges faced by researchers, semantic matchmaking and QoS optimisation. Semantic matchmaking aims to discover interoperable web services that can interact with each other to provide rich functionalities through language understanding and reasoning. QoS optimisation aims to optimise the non-functional requirement of service users, e.g., minimum cost, maximal reliability. Many scholars have looked into QoS optimisation problems in QoS-aware web service composition applying AI planning and Evolutionary Computation techniques. To meet users' requirement, one often needs to consider both semantic matchmaking quality and QoS simultaneously. Existing works on web service composition often concerns either semantic web  service composition or QoS-aware web service composition. However, there are few works concerns both semantic matchmaking quality and QoS at the same time and achieve a more desirable tradeoff in consideration of both sides. Therefore, In this paper, proposed a general comprehensive quality model for semantic matchmaking quality and QoS. This model is also suitable to be tackled through EC algorithms, and we develop a PSO-based service composition approach with explicit support for the comprehensive model, which can generate a more desirable balance in considering semantic matchmaking quality and QoS requirement by comparing existing QoS evaluation model. We also conduct an experiment shows that our PSO-based method performs better in finding more optimised solution by comparing one existing GP-based method.

@@

\textit{Web service composition} pertains to a combination of multiple web services to provide a value-added composition service that accommodates customers' arbitrarily complex requirements. This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems. Due to the increasing number of large-scale enterprise applications, the number of Web services has increased substantially and unprecedentedly. Therefore, manual and semi-automated web service composition are considered to be less efficient while automated web service composition enjoys less human intervention, less time consumption, and high productivity.

@@

Existing works on service composition focus mainly on addressing the one of challenges above. A lot of works have been conducted to optimise the quality of compositions under a pre-defined abstract workflow, which is generally considered as \textit{semi-automated Web service composition} approach \cite{parejo2008qos,bahadori2009optimal}. Meanwhile, many research works consider the possibility of generating a composition plan automatically in discovering and selecting suitable web services, which are considered to be NP-hard \cite{moghaddam2014service}. \textit{Semantic web services composition} is distinguished from the syntactic service composition, with the hope of eliminating conflicts by the semantic level of web services. In the past few years, substantial works have been done on semantic web service composition \cite{boustil2014semantic, mier2015integrated, bansal2016generalized}. However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously and achieved a desired balance.

The overall goal of this paper is to \textit{develop an comprehensive approach to automated QoS-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}. Particularly, this paper extends existing works of QoS-aware service composition by considering both QoS optimisation and semantic matchmaking quality optimisation in our proposed comprehensive quality model. Particle Swarm Optimisation (PSO) has show its promise in searching near-optimised service composition solutions \cite{da2016particle}. We will propose a PSO-based service composition approach with explicit support for our proposed quality mode. We will achieve three objectives in this work as follows:

@@

 \item To propose a PSO-based service composition algorithm that utilises the proposed quality model. To do that we will first propose a representation of semantic service composition, which can model the quality of semantic matchmaking and QoS together.

 \item To evaluate our proposed approach, we conduct experiment to compare our comprehensive quality model with one widely used QoS evaluation model, we also compare an one existing GP approach with our PSO-based approach using our comprehensive model. Both comparison utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}

@@

\cite{boustil2014semantic,mier2015integrated, bansal2016generalized} captures the semantics of web services' parameters using some kind of logic (e.g., description logic) for enabling semantic web service composition, where the number of web services or length of the graph is minimised to reach the optimised graph-based composition solutions. However, these approaches need to be improved for the scalability that considering a large number of web services, and the evaluation method does not fit properly for customers' complex requirements.

A heuristic service composition method is proposed by Qi et al. \cite{qi2010combining} for QoS-aware web service composiiton, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal for QoS. Obviously, there exists scalability problem for enumeration techniques.

Evolutionary Computation (EC) techniques are used to improve the scalability for solving NP-hard problems. Gupta et al. \cite{gupta2015optimization} employ an Genetic Algorithm to the problem of QoS-ware web service composition, and a set of binary strings are used as individuals, which demands to be decoded into composition solutions. Genetic Programming are employed by  \cite{yu2013adaptive} with direct representation of composition solutions, the overall quality of solutions are measured by a fitness function that is liable for penalising infeasible solutions. A hyper approach employs both a greedy search algorithm and Genetic Programming (GP) is introduced in \cite{ma2015hybrid} to generate locally optimised solution with functionality correctness. In particularly, the greedy search is used to generate directed acrylic graph as composition solutions, which is further transferred to the tree structure for initialisation and mutation using unfolding techniques. To eliminating the transformation process from DAG, A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of Directed Acyclic Graph(DAG) employing Graph-based evolutionary operators like crossover and mutation. PSO has shown its efficiency in solving combinatorial optimisation problems \cite{fukuyama2008fundamentals}, an indirect PSO-based approach was introduced in \cite{da2016particle}. An optimised queue is used as indirect representation as composition solution that decoding into Direct Acyclic Graph (DAG). These QoS-aware approaches does not consider semantic matchmaking quality, which could lead to over-general outputs to be produced by selected services, The finding is evidently supported by our first comparison experiment. In fact, customers' perspectives, application domains and ontology granularity all could have significant impact on the outputs requested by users. In some scenarios, the output is too broad to bear any specific meaning for the customers, even though those web services selected leads to a very good overall QoS.

Few works \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} employ EC technique for considering both semantic matchmaking quality and QoS simultaneously. Lecue et al. \cite{lecue2009optimizing} employ Genetic Algorithm for semi-automated web service composition considering semantic matchmaking quality and QoS, where the semantic matchmaking quality is measured by the quality of semantic links that requires formal definition of ontology in Description Logic. This evaluation takes huge cost and time for the domain experts to establish required ontology. Another GA-based approach work \cite{fanjiang2014semantic} employs a sequence of fitness functions are used in the binary selection of chromosomes, where semantic matchmaking quality is evaluate in two fitness functions considering concept similarity and parameter similarity respectively, but different semantic matchmaking types are ignored in the evaluation model. The work \cite{pop2009immune} as an immune-inspired web service composition approach employ indirect representation that a binary alphabet to encode a planning graph, where the semantic matchmaking quality is measured  by the similarity using information retrieval technique.

In summary, composition solutions from semantic web service composition \cite{boustil2014semantic,mier2015integrated, bansal2016generalized} does not consider QoS, and QoS-aware web service composiiton \cite{da2016particle,da2015graphevol,yu2013adaptive, gupta2015optimization,qi2010combining,ma2015hybrid} does not consider distinguished matchmaking quality in their fitness function. Few works do consider both quality aspects, but some limitations lie in semi-automated approach \cite{lecue2009optimizing}, less general semantic quality measurement \cite{lecue2009optimizing, pop2009immune}, or semantic matchmaking types ignorance \cite{pop2009immune}. In addition, experiments design for  \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} are not conducted using benchmark dataset for the scalability, only small datasets are utilised that might suffer scalability. Results analysis for \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} also do not evidently point out what desired balance could be reached by considering semantic matchmaking quality and QoS. Therefore, we proposed a general comprehensive quality model which achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS to fill the gaps discussed above, and then we proposed a POS-based method with explicit support for the comprehensive model, and evaluate its performance by comparing with one existing GP-based approach.

@@

The aim of web service composition is to fulfil customers' requirements, which could be denoted as a composition goal: $Comp.G(F(I_{T}, O_{T}), NF(QoS_{T}))$. This overall composition goal is demonstrated in two parts: functional part and non-functional part. The functional part is defined by given task input and desired task output. The nonfunctional part specifies overall QoS requirements. To accomplish the composition goal, two stages are involved, services discovery and service selection. Service discovery is to find matching web services: $S_{n}(F(I_{S}, O_{S}), NF(QoS_{S}))$ from a Service Repository: $\mathcal{S}$ $=  \{S_{1}, S_{2},..., S_{n} \}$ for the given $I_{T}$. If no atomic web service could satisfy the composition goal, a composition of web services will be found to meet $Comp.G$. To ensure the composition solution returns the desired $Comp.G$, we use a quality model that take care of QoS and semantic matchmaking quality.

@@

\section{Comprehensive Quality Model}\label{qswsc_approach}
In this section, we propose a general comprehensive quality-aware service model in consideration of both semantic matchmaking quality and QoS for semantic web service composition.

\subsection{Semantic Web Service matchmaking Type}\label{semantic Web service Discovery}
The semantic service matchmaking aims to discover appropriate services from service repository. A semantic web service is defined by $S(F(I_{S}\in C_{1}, O_{S}\in C_{2}), NF(QoS_{S}))$, where both Input and Output are linked to concept $C_{1}$ and $C_{2}$ in an ontology $O$ respectively, satisfying $O=\{C, Taxonomy\}$. A web service matching process is to match the output and input concepts of two services according to the Taxonomy within an ontology. To measure the quality of semantic matchmaking, different matching levels are typically considered in the literature \cite{paolucci2002semantic}. To understand these levels, let us define two web services associated with concept-related parameters in a particular domain. $S_{1}$ $(F(I_{S_1}\in C_{1}, O_{S_1}\in C_{2}), NF(QoS_{S_1}))$ and  $S_{2}$ $(F(I_{S_2}\in C_{3}, O_{S_2}\in C_{4}), NF(QoS_{S_2}))$ and an ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$. The matching levels to be considered are:

\begin{itemize}
\item \textit{Exact} ($\equiv$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Exact match ($ O_{S_1} \in S_{1} \equiv I_{S_2} \in S_{2}$), if  Concept $C_{2}$ and Concept $C_{3}$ are equivalent.
\item \textit{Plugin} ($\sqsubseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Plugin match ($O_{S_1} \in S_{1} \sqsubseteq_{n} I_{S_2} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of children concepts ($n=1$ stands for direct children).
\item \textit{Subsume} ($\sqsupseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Subsume matched($O_{S_1} \in S_{1} \sqsupseteq_{n} I_{S_2} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of  Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of parent concepts ($n=1$ stands for direct parent).
\item \textit{Fail} ($\perp$). Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are not matched (Fail) ($O_{S_1} \in S_{1} \perp I_{S_2} \in S_{2}$), if none of the previous matches discovered.
\end{itemize}

@@

\subsection{Comprehensive Quality Model}\label{qualityModel}
We propose a comprehensive quality model to evaluate the overall quality of semantic web service composition. This model overcome the disadvantages of current prevailing QoS-aware optimisation that ignores quality of semantic matchmaking.

@@

\textbf{Semantic web matchmaking quality model}. Due to that the discretisational characteristics of different match types and values assigned to matching types are driven by the cost of data integration and manipulation \cite{lecue2009optimizing}, partial ordering match types are considered to be one factor for quality of parameter matchmaking, denoted as $mt_{p}$,  For example, Exact matching type demands less time for computation compared to that of Plugin match. Another factor in our proposed model is concept similarity, which could be evaluated based on the edge counting method defined in \cite{shet2012new}. This formula (\ref{equation1}) is used to estimate the concept similarity between matching parameters, which is denoted as $s_{p}$. Therefore, given the quality of parameter matchmaking type and quality of parameter concept similarity, the quality of parameter matchmaking is defined by Formula (\ref{equation2}), where the value of $mt_{p}$ follows the same settings in \cite{lecue2009optimizing}. Particularly, 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection).

\begin{equation}
s_{p}{=} \frac{2N \cdot e^{-\lambda L/D} }{N_{1}+N_{2}}
\label{equation1}
\end{equation}

@@

Further more, since semantic web service link represent services connections, where quality of semantic web service link $(sm_{L})$ is considered to be semantic matching quality on service level by the aggregation of parameter matchmaking quality. Therefore, $sm_{L}$ is defined in formula (\ref{equation3}), where $sm_{L}$ and $s_{L}$ are the average value of all involved $mt_{p}$ and $s_{p}$ respectively.

@@

\textbf{Comprehensive quality model}. The comprehensive quality model consider both semantic matchmaking quality and QoS. The semantic matchmaking quality refers to $sm_{L}$. Consequently, the comprehensive quality model is defined in Formula (\ref{equation4}), which could be further broken down into Formula (\ref{equation5}). 
\begin{equation}
\label{equation4}
cq \stackrel{.}{=} (sm_ {L}, \  QoS_ {s})
\end{equation}
\begin{equation}
\label{equation5}
cq \stackrel{.}{=} (mt_ {L}, \  s_ {L}, \  a_{s},\  r_{s},\  c_{s},\  t_{s})
\end{equation}

\textbf{Semantic matchmaking quality aggregation}. The quality aggregation is defined based on the constructs of composition web services in consideration of semantic matchmaking quality and QoS. The quality on composition solution is further calculated by following the formula (\ref{equation6})(\ref{equation7}), and QoS aggregation are discussed in Sect. \ref{Quality of Service and Composition Constructs}

@@

We defined our semantic web service composition representation as a weighted graph $WG = (V, E)$, where $V$ is a set of services as vertex: $V=\{S1, S2...Sn \}$ and $E$ is a set of edges $E = \{e_{1}, e_{2},... e_{n} \}$. Each edge is considered to be a semantic web service link $sm_{L}$ , so each edge $e$ is consisting of a pair of quality values, $mt_{L}$ and $s_{L}$ as weigths. Here we provide an example of semantic web service composition, which is described in Fig. \ref{wscs}. The data of composition web service flows from the start to the end, where five web services involved and linked with each other using edge connections. Besides that, weights are calculated for all edges $e_{1}, e_{2},... e_{n}$.

@@

PSO has shown its efficiency in solving combinatorial optimisation problems \cite{fukuyama2008fundamentals}. Therefore, we will employ a PSO-based approach, which is considered to be simple and efficient without penalising or repairing that often required by GP \cite{da2016particle}. Fig. \ref{overview} shows the overview of our approach with five steps. Step 1: The composition process is triggered by a composition goal defined in Subsection \ref{problemDes}, which describes customers requirements both semantic matchmaking quality and QoS. Step 2: This composition goal are used to discover all relevant web services, which lead to a shrunken service repository that is subsequently used by PSO as a searching space. Step 3: A weighted graph representation is randomly built up from the an initial service queue that mapped to the particle's location, interleaving with semantic matchmaking process utilising ontology-based index cache. In the weighted graph, graph edges are assigned with semantic matchmaking quality as weights. Step 4: The fitness value of the weighted graph is evaluated to update the position of particle under PSO algorithm in Sect. \ref{pso_algorithm}, where the position is mapped to the index of service queue. later on, the updated service queue is used to decode a new weighted graph as the composition solution. Step 4. Lastly, the best position found in the searching space is selected and decode into the final optimised solution. This PSO-based approach is similar to \cite{da2016particle}, but we employ weighted graphs as a different solution presentation with explicit support for the proposed quality model.

\subsection{Ontology-based Index Cached Optimisation}\label{indexCache}
In PSO, particles represent weighted graphs with edges and vertices associated with quality of semantic web service matchmaking and QoS respectively, the bottlenecks of generating weighted graph lie in building edges and nodes, which are related to the cost of semantic quality calculation and the size of service repository respectively. To effectively construct weighted graphs, we pre-calculate semantic matchmaking quality. The key idea of the index is to create a map using a pair of keys, output-related concepts and potentially matched input-related concepts with considering different levels of match types, and the map values stored $mt_{p}$ and $mt_{s}$. Meanwhile, this index size could also be reduced by only considering the concepts related in the shrunken service repository, which means the index cache is filtered by those task-relevant web services. This optimised cache also contributes to less and constant time for weighted graphs building through the whole evolutionary process.

@@

\begin{algorithm}
 \setlength\hsize{0.9\linewidth}
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \SetKwFunction{generateWeightedGraph}{generateWeightedGraph}
 \SetKwProg{Procedure}{Procedure}{}{}
 \LinesNumbered
 \SetNlSty{}{}{:}
 \Input{relevant Web services $rws$}
 \Output{Optimised service queue $queue$,Optimised Weighted Graph $OPTWG$}
 Map each relevant service to an index in the particle's position vector\;
 Randomly initialise each particle in the swarm\;
  \While {max. iterations not met}{
     \ForEach{particles in the swarm}{
     $queue \leftarrow$ map service in a descending order by particle's position vector\;
     $WG \leftarrow$ $generateWeightedGraph$()\;
	 Calculate the $WG$ fitness value\;
